### 2020-06-26 Documents/ESA/sections/Intro.tex

    Based on the successes of the swarm control and MARL communities,
    a natural question to ask is whether the promises of these
    disciplines may be unified. Such a combination would radically
    improve the capabilities of autonomous system. Ultimately such a
    system must be driven under the influence of control inputs to
    perform given tasks. Examples of this might be: forming around
    individual components of space debris and moving them to a desired
    location (e.g.~a bin), or relocating to multiple areas in a
    disaster zone to provide immediate relief. For such tasks to be
    achieved in dynamic environments, which is typically the case, the
    system must be able to constantly adapt its approach and respond
    accordingly. Given these considerations, the problem may be stated
    as follows

    \begin{enumerate}
    	\item A population of robots is given a goal which must be
          achieved, which can often be deconstructed into a set of
          smaller tasks, to be executed simultaneously.
    	\item These are to be performed in a dynamic environment with
          obstacles present and where the number of tasks, and their
          priorities may be in constant flux.
    	\item The agents in the system must, therefore, make decisions
          collectively which \fb{will in the system achieving?} the given
          goals. Due to the dynamic quality of the problem, these
          decisions may need to be evaluated online and in a
          decentralised fashion, as it may not be possible for a
          centralised decision maker to communicate with all agents.
    	\item It is desirable, therefore, to control the dynamical
          behaviour of a system composed of agents who learn and adapt
          through interactions with each other. In addition, to ensure
          the safe operation of the system, properties such as state
          and control constraints must be satisfied.
    \end{enumerate}

>>>>

    Based on the successes of the swarm control and MARL communities,
    a natural question to ask is whether the promises of these
    disciplines may be unified. Such a combination would radically
    improve the capabilities of autonomous system. Ultimately such a
    system must be driven under the influence of control inputs to
    perform given tasks. Examples of this might be: forming around
    individual components of space debris and moving them to a desired
    location (e.g. a bin), or relocating to multiple areas in a
    disaster zone to provide immediate relief. For such tasks to be
    achieved in dynamic environments, which is typically the case, the
    system must be able to constantly adapt its approach and respond
    accordingly. Given these considerations, the problem may be stated
    as follows

    \begin{enumerate}
    	\item A population of robots is given a goal which must be achieved, which can often be
    	deconstructed into a set of smaller tasks, to be executed simultaneously. 
    	\item These are to be performed in a dynamic environment with obstacles present and where
    	the number of tasks, and their priorities may be in constant flux.
    	\item The agents in the system must, therefore, make decisions collectively which will result
        in the system achieving the given goals. Due to the dynamic quality of the problem, these
        decisions may need to be evaluated online and in a decentralised fashion, as it may not be
        possible for a centralised decision maker to communicate with all agents. 
        \item It is desirable, therefore, to control the dynamical behaviour of
    	a system composed of agents who learn and adapt through interactions with each other. In
    	addition, to ensure the safe operation of the system, properties such as state and control
    	constraints must be satisfied.
    \end{enumerate}

### 2020-06-26 Documents/ESA/sections/LitReview.tex

\begin{enumerate}
    \item {\em Distributed}. It will often be the case that a
      multi-agent system must spread out across a large area or
      operate in regions where communication is limited. As such it is
      beneficial that such a system does not rely too heavily on
      communication with a central body. The individual agents must,
      therefore, be able to make their own decisions and act as
      independent entities.  Aside from the advantage of
      communication, this ensures that the system is not tied to a
      single point of failure; in a system governed by a centralised
      decision maker, any faults in the central body propagates
      throughout the group. Of course, this comes at the price of
      computational load - if the agents are required to act
      independently, they must possess the resources to do so. The
      term distributed should not be confused with decentralised. The
      latter refers to a regime in which agents all communicate with
      one another before making a decision.  Whilst this is preferable
      to a centralised decision maker in terms of the requirement for
      one entity to communicate with all agents, it still places a
      high cost on the requirement that agents be in constant
      communication with one another. In fact it may pose the
      additional risk that if any agent in the team fails, the whole
      pipeline falls apart. Distributivity, on the other hand,
      requires that agents make independent decisions so that, though
      agents may communicate with each other, they are still able to
      operate when this is not possible.

    \item {\em Generality}. MAS come in many different flavours; sometimes a
      small group of heterogeneous
      %(agents with different capabilities)
      agents may be required to perform a delicate task
      whilst in others, it may be required that a large population of
      homogeneous
      %(all of the same type)
      agents perform multiple tasks
      simultaneously. Indeed the same MAS may have to adapt its
      strategy whilst in the middle of a task. It would be a hindrance
      if the agents were required to be reprogrammed with a completely
      different control methodology each time the situation changes
      slightly. It would be preferable if the method could apply to
      all different types of scenarios, with homogenous or
      heteregeneous agents, with single tasks or multiple, in any
      environment with only minor customisation required. Better still
      if the agents are able to adapt themselves to the specifics of
      the scenario.

\item {\em Low Computational Load}. As mentioned in the previous chapter, a
  MAS will often be used in complex situations, many of which will be
  too dangerous for human intervention. As such, the system will be
  required to carry out its tasks online. For this reason, it is vital
  that the control method be one which produces low computational load
  - especially where the time frame for adjusting agent behaviour is
  limited. Monetary concerns also play a part in this metric; it would
  not do to impose that every member of the team be equipped with high
  performance computing power as this would likely fall outside of the
  budget of any practical usage.

    \item {\em Robustness}. Particularly for physical robots, a MAS
      should be able to operate in situations which present sensor
      noise, communication noise, latency, and environmental
      disturbances. This is rather important in unseen environments
      where full a priori knowledge of the map cannot be assumed.

    \item {\em Scalable}. This is mentioned last since the ability for
      a MAS to scale comes from its distributivity and low
      computational load. Scalability is the capacity for any method
      of controlling a MAS to successfully operate as the size of the
      team increases. This, of course, is related to the complexity of
      the algorithms involved. However, it should be noted that it is
      not always required that a MAS be formed of dozens (or even
      hundreds) of agents. Depending on the task at hand (e.g. robotic
      surgery), it may be beneficial for fewer, more capable agents to
      perform the task, rather than a large population.
\end{enumerate}

@@

Game Theory has a rich history when considering an understanding of
multi-agent systems and it is impossible to examine MAS without an
understanding of Game Theory. These begin in economics but have found
a strong application in computation due to the rising need for
distributed systems. Game Theory, therefore, branches across all of
the categories in this chapter although its synergy with swarms
requires development\fr{)?} since Dec-POMDP \fr{not yet defined} and MARL methods have both base
their theory upon the foundations of Game Theory.

\fr{we might want to motivate the restriction to partial observability. Dimension to add to the presentation of MAS?}

@@

POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an
optimal solution \fr{to what?} is found by fixing the strategy (a
manner of selecting an action \cite{Rizk2018}) of all agents except
one. The optimal strategy of the chosen agent is then computed. This
is fixed so that the next agent may determine its optimal
strategy. This process is iterated over all agents in a process known
as Alternating Maximisation \cite{Ray2010}. By choosing strategies
which maximise a common payoff, a globally optimal solution can be
found.

Similarly Bayesian Games is a game theoretic approach with incomplete
information (thus it is sometimes referred to as an ‘incomplete
information game’). This allows for a POSG to be approximated by a
sequence of smaller, more tractable games
\cite{Emery-Montemerlo}. However, iterating through the entire team of
agents to find an optimal solution is a lengthy process and does not
allow for immediate actions in dynamic situations. To address this,
\cite{Ray2010} propose to place distinct payoffs on each agent and to
consider team formation based on social hierarchy as well as preferred
partners. This allows the complexity of the problem to be broken down
into smaller game units and also provides a clear order in which the
games are to be played. This minimises the interference across robots
and allows for more immediate action to be taken by agents who choose
their strategy early on, while leaving more passive tasks for those
later in the sequence.

The Bayesian Game formulation therefore provides a strong candidate
for rapid task re-allocation and dynamic decision making. However, as
found by Dai et. al \cite{Dai2018} this is conditional on an
understanding by each robot of the strategy of others, which in turn
requires adequate communication between robots. Therefore, the game
theoretical formulation will fail where communication is not possible
amongst team members. However, the addition of heuristics, such as
deep learning, may be able to advance an agent’s ability to recognise
the strategies taken by other members of its team without the need for
significant explicit communication.

@@

\begin{itemize}
    \item Stability, that a system will return to the desired setpoint (or within a neighbourhood) if
    perturbed.

    \item Robustness, that a system will perform its function in the presence of uncertainty and
    noise

    \item Optimality, that the system will achieve some defined function

    \item Feasibility, that the controller will always be able to generate a control law which
    satisfies the desired properties.
\end{itemize}

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control communnity is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
those which are particularly relevant to this study and review them in this section.

\subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}

Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
categories: decentralised control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only considers the case in which a
centralised controller has access and can manipulate multiple agents at once.

@@

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations for stochastic forward processes (such as swarm foraging) in which, as the number of
agents tends to infinity, the true macroscopic motion of the system tends to these equations.
Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
ability to develop control laws. In \cite{Li2017}, Li et al show that these models can be used to
develop control laws for robots in a swarm and drive them towards a target distribution. The method
is shown to perform accurately both in simulation and on real robots. The advantage is that
guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
distribution. However, there appears to be significant scope to expand upon this methodology from a
safety perspective. To begin with, the method does not consider inter-agent interactions and
therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
considered, although collisions are avoided by having the robot simply move in the opposite
direction when encountering an obstacle. It is here that the mean-field models are not as strong
since they do not take these local interactions into account. It must be noted, however, that Inoue
et al have identified this problem and are currently working towards its incorporation into the
model.

@@

It is clear that each method presents its own set of advantages and disadvantages. In fact, the
greater contributions are made from a unification of techniques (e.g. game theoretic control) which
leverage the strengths of one technique to mitigate the drawbacks of another. To this end, we
consider the unification of swarm control and multi-agent learning. The aim is to unify the
strengths of swarm theory, MPC and game theory to study populations of agents who can make
decisions on an individual basis but perform tasks through large scale collaboration. In the
subsequent chapters, we propose a line of research which explores the properties of a system as well
as establishing practical control methodologies along the way.

>>>>

\begin{enumerate}
    \item {\em Distributed}. It will often be the case that a multi-agent system must spread out
across a large area or operate in regions where communication is limited. As such it is beneficial
that such a system does not rely too heavily on communication with a central body. The individual
agents must, therefore, be able to make their own decisions and act as independent entities. Aside
from the low communication load, this ensures that the system is not tied to a single point of
failure; in a system governed by a centralised decision maker, any faults in the central body
propagates throughout the group. Of course, this comes at the price of computational load - if the
agents are required to act independently, they must possess the resources to do so. The term
distributed should not be confused with decentralised. The latter refers to a regime in which agents
all communicate with one another before making a decision. Whilst this is preferable to a
centralised decision maker in terms of the requirement for one entity to communicate with all
agents, it still places a high cost on the requirement that agents be in constant communication with
one another. In fact it may pose the additional risk that if any agent in the team fails, the whole
pipeline falls apart. Distributivity, on the other hand, requires that agents make independent
decisions so that, though agents may communicate with each other, they are still able to operate
when this is not possible.
    \item {\em Generality}. MAS come in many different flavours; sometimes a small group of
heterogeneous  (agents with different capabilities) agents may be required to perform a delicate
task whilst in others, it may be required that a large population of homogeneous (all of the same
type) agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
strategy whilst in the middle of a task. It would be a hindrance if the agents were required to be
reprogrammed with a completely different control methodology each time the situation changes
slightly. It would be preferable if the method could apply to all different types of scenarios, with
homogenous or heteregeneous agents, with single tasks or multiple, in any environment with only
minor customisation required. Better still if the agents are able to adapt themselves to the
specifics of the scenario.
    \item {\em Low Computational Load}. As mentioned in the previous chapter, a MAS will often be
used in complex situations, many of which will be too dangerous for human intervention. As such, the
system will be required to carry out its tasks online. For this reason, it is vital that the control
method be one which produces low computational load - especially where the time frame for adjusting
agent behaviour is limited. Monetary concerns also play a part in this metric; it would not do to
impose that every member of the team be equipped with high performance computing power as this would
likely fall outside of the budget of any practical usage.
    \item {\em Robustness}. Particularly for physical robots, a MAS should be able to operate in
situations which present sensor noise, communication noise, latency, and environmental disturbances.
This is rather important in unseen environments where full a priori knowledge of the map cannot be
assumed.
    \item {\em Scalable}. This is mentioned last since the ability for a MAS to scale comes from
its distributivity  and low computational load. Scalability is the capacity for any method of
controlling a MAS to successfully operate as the size of the team increases. This, of course, is
related to the complexity of the algorithms involved. However, it should be noted that it is not
always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the task
at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to perform the
task, rather than a large population. 
\end{enumerate}

@@

Game Theory has a rich history when considering an understanding of multi-agent systems and it is
impossible to examine MAS without an understanding of Game Theory. These begin in economics but have
found a strong application in computation due to the rising need for distributed systems. Game
Theory, therefore, branches across all of the categories in this chapter although its synergy with
swarms requires development) since Dec-POMDP (Decentralised Partial Observable Markov Decision
Processes) and MARL methods have both base their theory upon the foundations of Game Theory.

@@

POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution to a multi-agent
decision making problem is found by
fixing the strategy (a manner of selecting an action \cite{Rizk2018}) of all agents
except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
next agent may determine its optimal strategy. This process is iterated over all agents in a process
known as Alternating Maximisation \cite{Ray2010}. By choosing strategies which maximise
a common payoff, a globally optimal solution can be found.

Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
sometimes referred to as an `incomplete information game’). This allows for a POSG to be
approximated by a sequence of smaller, more tractable games
\cite{Emery-Montemerlo}. However, iterating through the entire team of agents to
find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
situations. To address this, \cite{Ray2010} propose to place distinct payoffs on each
agent and to consider team formation based on social hierarchy as well as preferred partners. This
allows the complexity of the problem to be broken down into smaller game units and also provides a
clear order in which the games are to be played. This minimises the interference across robots and
allows for more immediate action to be taken by agents who choose their strategy early on, while
leaving more passive tasks for those later in the sequence.

The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
dynamic decision making. However, as found by Dai et al. \cite{Dai2018} this is
conditional on an understanding by each robot of the strategy of others, which in turn requires
adequate communication between robots. Therefore, the game theoretical formulation will fail where
communication is not possible amongst team members. However, the addition of heuristics, such as
deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
members of its team without the need for significant explicit communication.

@@

\begin{itemize}
    \item {\em Stability}: a system will return to the desired setpoint (or within a neighbourhood) if
    perturbed.

    \item {\em Robustness}: a system will perform its function in the presence of uncertainty and
    noise

    \item {\em Optimality}: the system will achieve some defined function

    \item {\em Feasibility}: the controller will always be able to generate a control law which
    satisfies the desired properties.
\end{itemize}

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control community is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
those which are particularly relevant to this study and review them in this section.

\subsection{Distributed Model Predictive Control} \label{sec::Distributed_MPC}

Rawlings et al. \cite{rawlings2017model} divide the problem of distributed control into four distinct
categories: decentralised control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only considers the case in which a
centralised controller has access and can manipulate multiple agents at once. This immediately
violates the desired property of distributivity.

@@

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations for stochastic forward processes (such as swarm foraging) in which, as the number of
agents tends to infinity, the true macroscopic motion of the system tends to these equations.
Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
ability to develop control laws. In \cite{Li2017}, Li et al. show that these models can be used to
develop control laws for robots in a swarm and drive them towards a target distribution. The method
is shown to perform accurately both in simulation and on real robots. The advantage is that
guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
distribution. However, there appears to be significant scope to expand upon this methodology from a
safety perspective. To begin with, the method does not consider inter-agent interactions and
therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
considered, although collisions are avoided by having the robot simply move in the opposite
direction when encountering an obstacle. It is here that the mean-field models are not as strong
since they do not take these local interactions into account. It must be noted, however, that the authors have identified this problem and are currently working towards its incorporation into the
model.

@@

It is clear that each method presents its own set of advantages and
disadvantages. In fact, the greater contributions are made from a
unification of techniques (e.g., game theoretic control) which leverage
the strengths of one technique to mitigate the drawbacks of
another. To this end, we consider the unification of swarm control and
multi-agent learning. The aim is to unify the strengths of swarm
theory, MPC and game theory to study populations of agents who can
make decisions on an individual basis but perform tasks through large
scale collaboration. In the subsequent chapters, we propose a line of
research which explores the properties of a system as well as
establishing practical control methodologies along the way.

\fr{\textbf{what about some use cases/application scenarios.}}

### 2020-06-26 Documents/ESA/sections/ProposedResearch.tex

                  \fr{this is already attempted in the currect
                    research section, isn't it?}

@@

        \fr{we analyze each topic in a section \ldots}

@@

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
    	\caption{ \label{fig::DynamicalBehaviours} Different types of
          dynamial behaviour displayed by learning agents. a)
          Convergence to a unique fixed point in the upper right
          corner (1, 1). This fixed point is unique, in that all
          trajectories, regardless of initialisation, will converge to
          this point \cite{Tuyls2006AnGames}. b) Limit Cycle, the
          trajectories converge to cyclic behaviour c, d) Chaotic
          behaviour, here small deviatons in the initial conditions
          can grow exponentially \cite{Sanders2018}.}
    \end{figure}

@@

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al \cite{Hu2019}.
    	Here, the solid and dotted lines represent the evolution of thhe expectation of Q-values of
    	two actions across a population of 50 or 999 agents respectively who are trained on an
    	iterated Stag Hunt game. The circled and crossed
    	lines represent the dynamics of these Q-values as predicted by the system of equations
    	derived in the paper. These are seen to closely match the results of the numerical
    	experiments.}
    \end{figure}

>>>>

                  \fr{this is already attempted in the current
                    research section, isn't it?}

@@

	The remainder of this chapter analyses each of these topics in turn, providing suggestions for
	the course of research.
        \fr{we analyze each topic in a section \ldots}

@@

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
       displayed
    	by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
    	Convergence
    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
    	that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
    	exponentially. b-d drawn from \cite{Sanders2018}}
    \end{figure}

@@

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al. \cite{Hu2019}.
    	Here, the solid and dotted lines represent the evolution of the expectation of Q-values of
    	two actions across a population of 50 or 999 agents respectively who are trained on an
    	iterated Stag Hunt game. The circled and crossed
    	lines represent the dynamics of these Q-values as predicted by the system of equations
    	derived in the paper. These are seen to closely match the results of the numerical
    	experiments.}
    \end{figure}

### 2020-06-26 Documents/ESA/sections/ShortTermGoals.tex

    Here, $G, \rho, \eta, \mu$ are correlation functions, generated
    due to the averaging process (see Appendix
    \ref{app::ResearchSummary}). We now analyse the stability of this
    dynamical system by linearising about a fixed point. This yields
    the requirement that a fixed point $x^*$ satisfy
%
    \begin{equation}
    0 = x^* \left[\Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \sqrt{\Gamma} \tilde{\alpha} \tau \mu_x \right].
    \end{equation}

    The implication here is that the resulting value of $x^*$ can take two solutions. However, one of these is $x^* = 0$, which is found to rarely occur, while the second solution contains a term $\sqrt{\Gamma}$, which would yield complex values. If this is true, then it would imply that the learning algorithm will rarely converge for values of $\Gamma < 0$. Numerical experiments will shed more light on the likelihood of convergence. If this ansatz turns out to be incorrect (i.e., we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.

    We take the Fourier transform of this system \ref{} to determine the long term behaviour of the system
    after a disturbance. To neglect all transient behaviour, we consider the equation at $\omega =
    0$

@@

\begin{enumerate}
    \item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
    it does not affect the long term behaviour of the system (it does not appear in (
    \ref{eqn::EOM})).
    \item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
    over.
    \item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
    (variables are the payoff elements) with covariance parameterised by $\Gamma$.
    \item Initialise the agents with random initial conditions
      (i.e., random action probabilities).
    \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
    \item Every 100 iterations, check to see if the action
      probabilities have changed significantly.  If not (i.e., the
      change over the last 100 iterations is less than 1\%) the
      learning process is considered to have converged.

>>>>

    Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
    and the notation $\tilde{\cdot}$ denotes a term which has been scaled with respect to $N$ (see
    Appendix \ref{app::ResearchSummary} for method and notation). We now analyse the stability of
    this dynamical system by linearising about a fixed point. This yields the requirement that a
    fixed point $x^*$ satisfy

    \begin{equation}
    0 = x^* \left[\Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \sqrt{\Gamma} \tilde{\alpha} \tau \mu_x \right].
    \end{equation}

    The implication here is that the resulting value of $x^*$ can take two solutions. However, one
    of these is $x^* = 0$, which is found to rarely occur \cite{Coolen2005}, while the second solution
    contains a term $\sqrt{\Gamma}$, which would yield complex values. Such a result, of course, is
    not possible for a quantity denoting probabilities and so it appears that the theory cannot hold
    for $\Gamma < 0$. However, numerical experiments will shed light on the likelihood of
    convergence and the islands of stability in parameter space for this region.

    We take the Fourier transform of this system to determine the long term behaviour of the system
    after a disturbance. To neglect all transient behaviour (high frequency disturbances), we
    consider the equation at $\omega = 0$

@@

\begin{enumerate}
    \item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
    it does not affect the long term behaviour of the system (it does not appear in (
    \ref{eqn::EOM})).
    \item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
    over.
    \item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
    (variables are the payoff elements) with covariance parameterised by $\Gamma$.
    \item Initialise the agents with random initial conditions (i.e. random action probabilities).
    \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
    \item Every 100 iterations, check to see if the action
      probabilities have changed significantly.  If not (i.e., the
      change over the last 100 iterations is less than 1\%) the
      learning process is considered to have converged.
